The Galactic Delay-Time Distribution of Type Ia Supernovae:\\ A Chemical Evolution Perspective

### 2023-02-09 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}
    \centering
    \includegraphics{figures/greggio05_dtd.pdf}
    \caption{Analytical DTDs computed by \citet{Greggio2005-AnalyticalRates}. The solid red curve represents the SD DTD for Chandrasekhar explosions, while the green and blue solid curves represent, respectively, the CLOSE and WIDE formulations of a DD DTD. The best-fit approximations for the DD DTDs (see Equation \ref{eq:greggio05-approx}) are represented by the dashed olive and cyan curves, respectively. All DTDs are normalized to unity.}
    \label{fig:greggio05-dtd}
    \script{greggio05_dtd.py}
\end{figure}

>>>>

% \begin{figure}
%     \centering
%     \includegraphics{figures/greggio05_dtd.pdf}
%     \caption{Analytical DTDs computed by \citet{Greggio2005-AnalyticalRates}. The solid red curve represents the SD DTD for Chandrasekhar explosions, while the green and blue solid curves represent, respectively, the CLOSE and WIDE formulations of a DD DTD. The best-fit approximations for the DD DTDs (see Equation \ref{eq:greggio05-approx}) are represented by the dashed olive and cyan curves, respectively. All DTDs are normalized to unity.}
%     \label{fig:greggio05-dtd}
%     \script{greggio05_dtd.py}
% \end{figure}
